Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-14 automatica/paper.tex
reviewed the DSSynth tool description
Signed-off-by: Lucas Cordeiro <lucasccordeiro@gmail.com>

In Step~1, the user selects the digital controller representation, which
can be a transfer function or a state-space model.  In Step~2, the
physical plant in the form of Equation~\eqref{eq:ode1} must be
given~\cite{astrom1997computer}.  Finally, in Step~3, the numerical
representation for the digital controller implementation must be set by the
user, i.e., the FWL format that defines the number of bits of the integer
and fractional parts as well as the dynamic range inputs.  The input 
provided by the user is a specification of the physical plant.

After that, the automated synthesis process starts with Step~A, where the
\tool translates the digital system specification from the MATLAB format
into an ANSI-C program.  In Step~B, our CEGIS engine is invoked to
synthesize the digital controller w.r.t.~the digital system specification. 
Finally, in Step~C, the synthesized digital controller is produced.  The
output generated by the \tool is the synthesized digital controller
represented either in transfer function or state-space equation.  The
synthesis is considered to be \emph{successful} if a digital controller is
correctly synthesized w.r.t.~FWL effects; otherwise, if any parameter is
incorrectly defined in previous steps, or if there is no solution (no
controller) for the respective physical plant (given the implementation
requirements), then the synthesis is considered to have \emph{failed}.

Our CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{ClarkeKL04}.  CBMC transforms the ANSI-C representation
of our closed-loop control system model into its internal representation (IR).  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT or SMT solver to solve verification conditions.  We~model FWL
effects, time discretization and the presence of quantization noise
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included in
CBMC~5.7 and is available for
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
\textcolor{red}{Lucas: I'll need support from Pascal to create this VirtualBoxOVA}
We further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script with
instructions to run all benchmarks and reproduce our
experiments.\footnote{\url{XXXXXXXXXX}}

@@

The entire implementation consists of $XXX$ and $XXX$ lines of C code in the naive and abstract
accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 
fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
module in CEGIS CBMC.  We evaluate \tool using $XXX$ SISO control system
benchmarks.

>>>>

In Step~1, the user selects the closed-loop digital control
system representation, which can be a transfer function or a state-space model.  
In Step~2, the physical plant (e.g., in the form of Equation~\eqref{eq:ode1}) must be
given~\cite{astrom1997computer}.  Finally, in Step~3, the numerical
representation for the digital controller implementation must be set by the
user, i.e., the FWL format that defines the number of bits of the integer
and fractional parts when using fixed-point arithmetic or half- and single-precision 
when using floating-point arithmetic as well as the dynamic range inputs.  The input 
provided by the user is a specification of the physical plant.

After that, the automated synthesis process starts with Step~A, where the
\tool~translates the digital system specification into an ANSI-C program.  
In Step~B, our CEGIS engine is invoked to
synthesize the digital controller w.r.t.~the digital system specification. 
Finally, in Step~C, the synthesized digital controller is produced.  The
output generated by the \tool~is the synthesized digital controller
represented either in transfer function or state-space equation.  The
synthesis is considered to be \emph{successful} if a digital controller is
correctly synthesized w.r.t.~FWL effects; otherwise, if any parameter is
incorrectly defined in previous steps, or if there is no solution (no
controller) for the respective physical plant (given the implementation
requirements), then the synthesis is considered to have \emph{failed}.

Our CEGIS engine is implemented as an integrated module within the C bounded
model checker (CBMC)~\cite{ClarkeKL04}.  CBMC transforms the ANSI-C representation
of our closed-loop control system model into its internal representation (IR).  We
instrument this IR for each synthesis or verification scenario accordingly,
and use CBMC as an oracle to answer our queries.  CBMC itself relies on an
underlying SAT or SMT solver to solve verification conditions.  We~model FWL
effects, time discretization and the presence of quantization noise
explicitly using CBMC's nondeterminism API (e.g., \texttt{nondet},
\texttt{CPROVER\_assume} intrinsic functions).  Our module is included into
CBMC~5.7 and is available for
download.\footnote{\url{https://github.com/diffblue/cbmc/archive/cbmc-5.7.zip}}
\textcolor{red}{Lucas: I'll need support from Pascal to create this VirtualBoxOVA}
We further created a VirtualBox OVA image with our tool pre-installed,
including our MATLAB-generated benchmarks and benchmark shell script with
instructions to run all benchmarks and reproduce our
experiments.\footnote{\url{XXXXXXXXXX}}

@@

The entire implementation consists of $XXX$ and $XXX$ lines of C code in the naive and abstract
accelerator back-ends, respectively, $XXXX$ lines of C code for utility functions such as interval, 
fixed- and floating-point arithmetic, as well as $1000$ lines of C++ code in the control synthesis
module in CEGIS CBMC.  We evaluate \tool~using $XXX$ SISO control system
benchmarks.
